\documentclass{article}
\usepackage[a4paper, margin=4cm]{geometry}
\usepackage[utf8]{inputenc}

\pagenumbering{gobble}
\begin{document}

\section*{List of Publications}

\begin{enumerate}
    \item \textbf{Suraj Srinivas}, Kyle Matoba, Hima Lakkaraju, Fran\c{c}ois Fleuret.
    ``Efficient Training of Low-Curvature Neural Networks", Neural Information Processing Systems (NeurIPS), 2022
    \item Tessa Han, \textbf{Suraj Srinivas}, Hima Lakkaraju,``Which Explanation Should I Choose? A Function Approximation Perspective to Characterizing Post hoc Explanations", Neural Information Processing Systems (NeurIPS), 2022
    \item Marwa El Halabi, \textbf{Suraj Srinivas}, Simon Lacoste-Julien.
    ``Data-Efficient Structured Pruning via Submodular Optimization", Neural Information Processing Systems (NeurIPS), 2022
    \item \textbf{Suraj Srinivas}, Andrey Kuzmin, Markus Nagel, Mart van Baalen, Andrii Skliar, Tijmen Blankevoort.``Cyclical Pruning for Sparse Neural Networks", Computer Vision and Pattern Recognition Workshops (CVPRW), 2022
    \item  \textbf{Suraj Srinivas}, Fran\c{c}ois Fleuret. ``Rethinking the Role of Gradient-based Attribution Methods in Model Interpretability", International Conference on Learning Representations (ICLR), 2021
    \item \textbf{Suraj Srinivas}, Fran\c{c}ois Fleuret. ``Full-Gradient Representation
    for Neural Network Visualization", Neural Information Processing System (NeurIPS), 2019
    \item \textbf{Suraj Srinivas}, Fran\c{c}ois Fleuret.``Knowledge Transfer with Jacobian Matching", International Conference on Machine Learning (ICML), 2018
    \item Akshayvarun Subramanya, \textbf{Suraj Srinivas}, R Venkatesh Babu, ``Estimating Confidence for Deep Neural Networks through Density modeling'', International Conference on Signal Processing and Communications (SPCOM), 2018
    \item \textbf{Suraj Srinivas}, Akshayvarun Subramanya, R. Venkatesh Babu. ``Training
    Sparse Neural Networks", Computer Vision and Pattern Recognition Workshops (CVPRW), 2017
    \item \textbf{Suraj Srinivas}, Ravi Kiran Sarvadevabhatla, Konda Reddy Mopuri, Nikita Prabhu, Srinivas SS Kruthiventi, R Venkatesh Babu. ``A taxonomy of deep convolutional neural nets for computer vision'', Frontiers in Robotics and AI
    \item \textbf{Suraj Srinivas}, R. Venkatesh Babu. ``Learning the Architecture of Deep Neural Networks", British Machine Vision Conference (BMVC), 2016
    \item \textbf{Suraj Srinivas}, R. Venkatesh Babu. ``Data-free Parameter Pruning for
    Deep Neural Networks", British Machine Vision Conference (BMVC), 2015

\end{enumerate}


\end{document}